DRAFT \\ From physical principles to classical and quantum \\ Hamiltonian and Lagrangian particle mechanics

### 2016-10-04 2015CompleteDerivation/pictures/temporalDof.tex
No need to use calculator package
Missing hats in the left part

\documentclass{standalone}
\usepackage{tikz}
\usetikzlibrary{calc}
\usepackage{calculator}
\begin{document}
	\begin{tikzpicture}[scale=0.4]

@@

		\draw[black,fill=green,fill opacity=0.1,draw opacity=.2,text opacity =1,text=black,rotate around={\phivar:($(h0)$)}] ($(h0)$) rectangle ($(h8)$) node[pos=.5, rotate=\phivar] {\large $dq\wedge dp$};

		\draw[black,fill=green,fill opacity=0.1,draw opacity=.2,text opacity =1,text=black,rotate around={0:($(h0)$)}] ($(h2)$) rectangle ($(h5)$) node[pos=.5] {\large $dt\wedge dE$};

>>>>

\documentclass{standalone}
\usepackage{tikz}
\usetikzlibrary{calc}
\begin{document}
	\begin{tikzpicture}[scale=0.4]

@@

		\draw[black,fill=green,fill opacity=0.1,draw opacity=.2,text opacity =1,text=black,rotate around={\phivar:($(h0)$)}] ($(h0)$) rectangle ($(h8)$) node[pos=.5, rotate=\phivar] {\large $d\hat{q}\wedge d\hat{p}$};

		\draw[black,fill=green,fill opacity=0.1,draw opacity=.2,text opacity =1,text=black,rotate around={0:($(h0)$)}] ($(h2)$) rectangle ($(h5)$) node[pos=.5] {\large $d\hat{t}\wedge d\hat{E}$};
